Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-31 WSSSPE2_report/WSSSPE2_review.tex
new comment

To enable a form of standardized crediting for developers of research software,
the group proposed to work towards a taxonomy for software-based
contributorship. The taxonomy should be derived from, or extend, existing
taxonomies for research impact and contributorship such as defined by CASRAI (in
particular based on the Wellcome-Harvard contributorship
taxonomy\footnote{Project CRediT, \url{http://credit.casrai.org/}}, VIVO, or
ISNI. An interesting measure of impact raised by the group was the {\em
betweenness centrality}, an indicator of a person's centrality (and hence,
importance) in a scientific collaboration. It is expected that developers of
research software often play such a central role. \choinote{cite VIVO or ISNI?}

@@

The WSSSPE2 workshop continues our experiment from WSSSPE1 in how we can
collaboratively build a workshop agenda. The differences in WSSSPE2 from WSSSPE1
are in using an existing service (EasyChair) to handle submissions and reviews,
rather than an ad hoc process, and using an existing service (well-sorted) to
allow collaborative grouping of papers into themes by all authors, reviewers,
and the community, rather than this being done in an ad hoc manner by the
organizers alone. \choinote{Are lightning talks a new feature in WSSSPE2?}
\katznote{yes, along with a change to breakout groups that were intended to
define actions, then potentially become longer lasting working groups to perform
those actions} \choinote{Since lightning talks is confirmed a new feature in
WSSSPE2, shall it be recorded somewhere in an earlier section?}

>>>>

To enable a form of standardized crediting for developers of research software,
the group proposed to work towards a taxonomy for software-based
contributorship. The taxonomy should be derived from, or extend, existing
taxonomies for research impact and contributorship such as defined by CASRAI (in
particular based on the Wellcome-Harvard contributorship
taxonomy\footnote{Project CRediT, \url{http://credit.casrai.org/}}, VIVO, or
ISNI. An interesting measure of impact raised by the group was the {\em
betweenness centrality}, an indicator of a person's centrality (and hence,
importance) in a scientific collaboration. It is expected that developers of
research software often play such a central role. %\choinote{cite VIVO or ISNI?}

@@

The WSSSPE2 workshop continues our experiment from WSSSPE1 in how we can
collaboratively build a workshop agenda. The differences in WSSSPE2 from WSSSPE1
are in using an existing service (EasyChair) to handle submissions and reviews,
rather than an ad hoc process, and using an existing service (well-sorted) to
allow collaborative grouping of papers into themes by all authors, reviewers,
and the community, rather than this being done in an ad hoc manner by the
organizers alone. \choinote{Are lightning talks a new feature in WSSSPE2?}
\katznote{yes, along with a change to breakout groups that were intended to
define actions, then potentially become longer lasting working groups to perform
those actions} \choinote{Since lightning talks is confirmed a new feature in
WSSSPE2, shall it be recorded somewhere in an earlier section?} \katznote{yes, please feel free to add something in the abstract and intro - maybe we also need a new section after keynotes for lightning talks?}
